---
title: "ARCHS4 Overview"
author: "Steve Lianoglou"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    css: mystyles.css
vignette: >
  %\VignetteIndexEntry{ARCHS4 Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

ARCHS4 is a project ([web site][archs4web] | [publication][archs4pub])
lead by [Alex Lachmann][lachmann] from [The Ma'ayan Lab][maayanlab] which aims
to reprocesses all of the human and mouse Illumina based (RNA) sequencing data
from [GEO][geo] and [SRA][sra] and make it available for exploratory data
analysis.

To facilitate that, the raw sequencing data is processed through the same
quantitation pipeline, which consists of [kallisto][kallisto] for quantitation
and ensembl gene annotations for the transcript models. These data are then
made available:

1. as binary files [for download][archs4dl]; and
2. via an [interactive exploratory analysis tool][archs4eda].

The scope of this package, for now, is to simply make all of the gene- and
transcript-level expression data easily queryable and retrievable to an analyst
within R.

[//]: # (Installation =========================================================)
```{r child = system.file("rmd", "installation.Rmd", package = "archs4")}
```

[//]: # (References ===========================================================)
```{r child = system.file("rmd", "references.Rmd", package = "archs4")}
```
